Ontario Graduate Scholarship: Plan of Study

### 2020-04-09 latex/ogs/main.tex
Rough Draft update: changed the goal to transitioning between VNHCs

When a gymnast is performing a swing-up routine on a bar, they do not kick their
feet at specified time intervals. Rather, a more natural human motion is to
swing their legs based on their current speed and position. In doing so, they
are able to generate enough momentum to perform backflips on the bar. When
controlling mechanical systems, standard practice is to have a robot's actuators
track a position dependent on time. Much like the gymnast, this tends to
produce unnatural motion. Furthermore, it is liable to timin errors if the
motion is interrupted in any way. The more recent techniques of virtual constraints 
can rectify these issues and produce realistic, biologically inspired motion.

Mechanical systems can have their motion constrained in two ways. Holonomic 
constraints restrict position, while nonholonomic constraints restrict
velocities (such as how a car cannot normally slide sideways). Previous research
has shown that one can enforce holonomic constraints through a robot's
actuators \cite{vhcs_for_el_systems}. These are called ``virtual holonomic
constraints" (VHCs). VHCs have been used to control walking robots \cite{stable-walking},
autonomous bicycles \cite{bicycle}, gymnastics robots \cite{xingbo-thesis}, and
snake robots \cite{snake-robot} among others. Likewise, in my 
master's thesis \textbf{TODO: HOW TO CITE?} I developed a general theory for
enforcing virtual nonholonomic constraints (VNHCs). I designed constraints which
injected energy into the gymnastics robot created by 
Wang \cite{xingbo-thesis}, enabling it to perform backflips on a bar.

@@

Mohammadi \textit{et.al.} showed that a single VHC can result in several motion
patterns, from which one pattern can be chosen if the robot is initialized with
a configuration that is ``close enough” to the desired motion pattern
\cite{manfredi-orbit-stabilization}. However, their method does not work for all
starting configurations of the robot. We propose to investigate a method to
stabilize and transition between desired motion patterns from any starting
configuration of the robot. Rather than using VHCs, we will use VNHCs to
generate these motions.

VNHCs have been studied for application to human-robot cooperation in
\cite{vnhc-human-robot-coop} and walking robots in \cite{vnhc-biped-robot}. Horn
\textit{et.al.} have also examined properties of VNHCs for general mechanical
systems \cite{hybrid_zero_dynamics_bipedal_nhvcs} and then applied their results
to walking robots. Our approach is novel since we will study VNHCs on general
mechanical systems with the aim of transitioning between desired motion patterns.

We will first study mathematical conditions under which on can transition
between two VNHCs. These conditions will allow us to create a control algorithm
to switch between motion patterns. After completing this mathematical
formulation, we will apply the results to the gymanstics robot built by Wang
\cite{xingbo-thesis}. We will use the theory to create control algorithms which
enable this robot to perform an entire gymnastics routine by transitioning
between different VNHCs.

>>>>

When a gymnast is performing a swing-up routine on a bar, they do not kick their
feet at specified time intervals. Rather, a more natural human motion is to
swing their legs based on their current speed and position. In doing so, they
are able to generate enough momentum to perform backflips on the bar. When
controlling mechanical systems, standard practice is to have a robot's actuators
track a position dependent on time. Much like the gymnast, this tends to
produce unnatural motion. Furthermore, it is liable to timing errors if the
motion is interrupted in any way. The more recent techniques of virtual constraints 
can rectify these issues and produce realistic, biologically plausible motion.

Mechanical systems can be constrained in two ways. Holonomic constraints
restrict position (for instance, car tires remain a fixed distance apart), while
nonholonomic constraints restrict velocities (such as how those tires cannot
slide sideways). Previous research has shown that one can enforce holonomic
constraints through a robot's actuators \cite{vhcs_for_el_systems}. These are
called ``virtual holonomic constraints" (VHCs). VHCs have been used to control
walking robots \cite{stable-walking}, autonomous bicycles \cite{bicycle},
gymnastics robots \cite{xingbo-thesis}, and snake robots \cite{snake-robot}
among others. These VHCs are a special case of the more general virtual
nonholonomic constraints (VNHCs); in my master's thesis \textbf{TODO: HOW TO
CITE?} I developed a general theory for enforcing VNHCs and designed
one which injects energy into the gymnastics robot created by Wang
\cite{xingbo-thesis}, thereby enabling it to perform backflips on a bar.

@@

Mohammadi \textit{et.al.} showed that a single VHC can result in several motion
patterns (also called ``orbits"), from which one specific motion can be chosen
if the robot is initialized with a configuration that is ``close enough” to it
\cite{manfredi-orbit-stabilization}. However, their method does not work for all
starting configurations of the robot. We propose to extend this work and 
investigate a method to stabilize and transition between two VNHCs, which should
also allow one to stabilize an orbit from any starting configuration.

VNHCs have been studied for application to human-robot cooperation
\cite{vnhc-human-robot-coop} and walking robots \cite{vnhc-biped-robot}. Horn
\textit{et.al.} have also examined properties of VNHCs for general mechanical
systems \cite{hybrid_zero_dynamics_bipedal_nhvcs} and applied their results
to stabilizing a chosen gait on walking robots. 
Our approach is novel since we will develop techniques to transition between  
VNHCs on general mechanical systems while maintaining safety constraints, 
rather than stabilizing a single VNHC.

We will first study mathematical conditions under which on can transition
between two VNHCs. These conditions will allow us to create a control algorithm
to switch between motion patterns. After completing this mathematical
formulation, we will test the theory on the gymanstics robot built by Wang
\cite{xingbo-thesis} by designing a gymnastics routine which is performed 
by transitioning between different VNHCs.
